Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-08 manuscript/supplements_rsfmri.Rmd
restructuring result section, correcting typos.

```{r "load packages", include=FALSE}

# load packages
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8

@@

library(sjPlot) #only works for HTML output
library(texreg) #works for Rmarkdown
library(knitr) # version 1.30

@@

# Methods
## Sample
```{r "tableSample", echo=FALSE}

tableSample <- readRDS(file = "../report/tab/tableSample.rds")

tab <-
  knitr::kable(
    tableSample,
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "Distribution of data points at months after intervention")
tab
```

```{r tableDescr, include=FALSE}
# table for descriptive statistics
tableDescr <- readRDS(file = "../report/tab/tableDescr.rds")

knitr::kable(
    tableDescr,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "BMI and mFD of participants acquired in each condition and time point")
```

@@

```{r fighistograms,fig.cap="Histograms of FC-QC correlations for different preprocessing schemes)", out.width="40%", eval=FALSE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%", eval=TRUE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

@@

```{r DMN2tp results age, sex, caption="DMN connectivity compared bl to fu, adjusted for age and sex", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), custom.model.names = c("R0", "R1"), float.pos = "h",  custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Group BARS", "Age", "Sex", "Timepoint x Group"),  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

@@

```{r DMN2tp results age sex mFD, caption="DMN connectivity compared bl to fu, adjusted for age, sex and mFD", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), custom.model.names = c("R0", "R1"), float.pos = "h",  custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Group BARS", "Age", "Sex", "logmFD", "Timepoint x Group"),  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

@@

```{r DMN3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 4, 8,9,5,6,7),custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Timepoint FU2", "Group BARS", "Age", "Sex","logmFD","Timepoint FU x Group", "Timepoint FU2 x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

@@

```{r Rew2tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), custom.coef.names=c("Intercept (BL, NBARS)","Timepoint FU", "Group BARS", "Age", "Sex", "Timepoint x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

@@

```{r Rew2tpadj results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 7, 4, 5, 6),custom.coef.names=c("Intercept (BL, NBARS)","Timepoint FU", "Group BARS", "Age", "Sex","logmFD","Timepoint x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

### Reward network for three timepoints, adjusted for age, sex, mean FD (Model 1b)
```{r calc rew three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC)
anvRew3tp=anova(R1,R0)
```
```{r Rew3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 4, 8,9,5,6,7),custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Timepoint FU2", "Group BARS", "Age", "Sex","logmFD","Timepoint FU x Group", "Timepoint FU2 x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
```{r Rew conn over three timepoints, echo=FALSE}
fig_Rewconn <- readRDS(file = "../report/fig/figRewconn.rds")
fig_Rewconn
```

@@

```{r DMN_BMIFD results, caption="Model 2a and 2b for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R1,R11), custom.coef.names=c("Intercept", "average BMI", "change BMI", "Age", "Sex","logmFD"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
#### Model 2c (adjusting for average and change in mFD)
```{r "DMN model mean+change of BMI+logmFD", eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~  mean.BMI + within.BMI + mean.logmFD + within.logmFD + Age_BL + Sex  + (1|subj.ID), data=final_FC)
R01 = lme4::lmer(mean_DMN_conn ~ mean.BMI + mean.logmFD + within.logmFD + Age_BL + Sex +(1|subj.ID), data=final_FC)
R02 = lme4::lmer(mean_DMN_conn ~ within.BMI + mean.logmFD + within.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R03 = lme4::lmer(mean_DMN_conn ~ mean.BMI  + within.BMI +  within.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R03 = lme4::lmer(mean_DMN_conn ~ mean.BMI  + within.BMI +  mean.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
anvwithinBMI=anova(R1,R01)
anvmeanBMI=anova(R1,R02)
anvmeanFD=anova(R1,R03)
anvwithinFD=anova(R1,R03)

@@

```{r DMN_BMI_splitFD results, caption="Model 2c for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R1), custom.coef.names=c("Intercept", "average BMI", "change BMI", "average mFD", "change mFD", "Age", "Sex"), custom.model.names = "R1", float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
\newpage
```{r, include = FALSE}

source("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /code_and_manuscript/code/tables.R")

ToolboxOutputList <- mk_DetailedLabelTab()
TableList_colname <- kableExtra::linebreak(c("Cluster","Number of voxels\n in cluster","\\% of cluster volume\nassigned", "Hemisphere","Area","\\% of area overlap\nwith cluster"))

@@

### Anatomical Labelling for models

```{r, echo=FALSE}
TableList[[1]]
TableList[[2]]
TableList[[3]]
TableList[[4]]
TableList[[5]]
TableList[[6]]
TableList[[7]]
TableList[[8]]
TableList[[9]]
```

>>>>

```{r "load packages", include=FALSE}
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8

@@

library(sjPlot) # only works for HTML output
library(texreg) # for works for Rmarkdown
library(knitr) # version 1.30

@@

# Methods
## Sample
```{r "tableSample", echo=FALSE}
tableSample <- readRDS(file = "../report/tab/tableSample.rds")
tab <-
  knitr::kable(
    tableSample,
    row.names = TRUE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "Distribution of data points at months after intervention")
tab
```

```{r tableDescr, include=FALSE}
# table for descriptive statistics
tableDescr <- readRDS(file = "../report/tab/tableDescr.rds")
knitr::kable(
    tableDescr,
    row.names = FALSE,
    format = "latex",
    booktabs = T,
    linesep = "",
    caption = "BMI and mFD of participants acquired in each condition and time point")
```

@@

```{r fighistograms,fig.cap="Histograms of FC-QC correlations for different preprocessing schemes)", out.width="100%", fig.align = "center", eval=FALSE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="100%", fig.align = "center", eval=TRUE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

@@

```{r DMN2tp results age, sex, caption="DMN connectivity compared bl to fu, adjusted for age and sex", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "Timepoint x Group"
  ),
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

@@

```{r DMN2tp results age sex mFD, caption="DMN connectivity compared bl to fu, adjusted for age, sex and mFD", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint x Group"
  ),
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

@@

```{r DMN3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4, 8, 9, 5, 6, 7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint FU x Group",
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

@@

```{r Rew2tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

@@

```{r Rew2tpadj results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 7, 4, 5, 6),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

### Reward network for three timepoints, adjusted for age, sex, mean FD (Model 1b)
```{r calc rew three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC)
anvRew3tp=anova(R1,R0)
```
```{r Rew3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4, 8, 9, 5, 6, 7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint FU x Group",
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```
```{r Rew conn over three timepoints, echo=FALSE}
fig_Rewconn <- readRDS(file = "../report/fig/figRewconn.rds")
fig_Rewconn
```

@@

```{r DMN_BMIFD results, caption="Model 2a and 2b for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R1, R11),
  custom.coef.names = c("Intercept", "average BMI", "change BMI", "Age", "Sex", "logmFD"),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```
#### Model 2c (adjusting for average and change in mFD)
```{r "DMN model mean+change of BMI+logmFD", eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~  mean.BMI + within.BMI + mean.logmFD + within.logmFD + Age_BL + Sex  + (1|subj.ID), data=final_FC)
R01 = lme4::lmer(mean_DMN_conn ~ mean.BMI + mean.logmFD + within.logmFD + Age_BL + Sex +(1|subj.ID), data=final_FC)
R02 = lme4::lmer(mean_DMN_conn ~ within.BMI + mean.logmFD + within.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R03 = lme4::lmer(mean_DMN_conn ~ mean.BMI  + within.BMI +  within.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R03 = lme4::lmer(mean_DMN_conn ~ mean.BMI  + within.BMI +  mean.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
anvwithinBMI=anova(R1,R01)
anvmeanBMI=anova(R1,R02)
anvmeanFD=anova(R1,R03)
anvwithinFD=anova(R1,R03)

@@

```{r DMN_BMI_splitFD results, caption="Model 2c for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R1), custom.coef.names=c("Intercept", "average BMI", "change BMI", "average mFD", "change mFD", "Age", "Sex"), custom.model.names = "R1", float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

\newpage
### Anatomical Labelling for models

Find in Table \@ref(tab:firstTab) to Table \@ref(tab:lastTab) with the detailed Output of the SPM Anatomy toolbox, version 2.2c. For Clusters without any labels, the toolbox was unable to assign any grey matter area.

```{r, include = FALSE}
ToolboxOutputList <- readRDS(file = "../report/tab/DetailedFCTableList.rds")
TableList_colname <- kableExtra::linebreak(c("Cluster","Number of voxels\n in cluster","\\% of cluster volume\nassigned", "Hemisphere","Area","\\% of area overlap\nwith cluster"))

@@

```{r "firstTab", echo=FALSE}
i = 1
TableList[[i]] <-
    ToolboxOutputList$EntryList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = TableList_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = ToolboxOutputList$CaptionList[i],
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down')) #%>%
    #kableExtra::landscape()
TableList[[1]] 
```

```{r, echo=FALSE}
TableList[[2]]
TableList[[3]]
TableList[[4]]
TableList[[5]]
TableList[[6]]
TableList[[7]]
TableList[[8]]
```

```{r "lastTab", echo=FALSE}
i = 9
TableList[[i]] <-
    ToolboxOutputList$EntryList[[i]] %>%
    knitr::kable(
      escape = FALSE,     # use font spec of latex with kableExtra
      col.names = TableList_colname,
      row.names = FALSE,
      format = "latex",
      booktabs = T,
      linesep = "",      # disable "\\addlinespace" at every 5th line
      #label = name_model[i],
      caption = ToolboxOutputList$CaptionList[i],
    ) %>%
    kableExtra::kable_styling(latex_options = c('scale_down')) #%>%
    #kableExtra::landscape()
TableList[[9]] 
```
